Verifying Spatial Properties of Array Computations

### 2017-04-17 oopsla17/introduction.tex
cleanup

\noindent
In the sciences, complex models are now almost always expressed as
computer programs. But how can a scientist have confidence that the
implementation of their model is as they intended? There is an
increasing awareness of the need for program verification in science
and the possibility of using (semi-)automated
tools~\cite{post2005computational,oberkampf2010verification,orchard2014computational}.
However, whilst program verification approaches are slowly maturing in
computer science they see little use in the natural and physical
sciences. This is partly due to a lack of training and awareness, but
also a lack of tools targeted at the needs of scientists. This
paper is part of a line of research on providing lightweight, easy-to-ue
verification tools targeted at common programming patterns in science, 
motivated by analysis of real code.

@@

We fix some terminology used throughout to describe
syntactic constructs.

>>>>

s\noindent
In the sciences, complex models are now almost always expressed as
computer programs. But how can a scientist have confidence that the
implementation of their model is as they intended? There is an
increasing awareness of the need for program verification in science
and the possibility of using (semi-)automated
tools~\cite{post2005computational,oberkampf2010verification,orchard2014computational}.
However, whilst program verification approaches are slowly maturing in
computer science they see little use in the natural and physical
sciences. This is partly due to a lack of training and awareness, but
also a lack of tools targeted at the needs of scientists. This
paper is part of a line of research on providing lightweight, easy-to-ue
verification tools targeted at common programming patterns in science,
motivated by analysis of real code.

@@

We fix some terminology for syntactic constructs in our target language.
